---
title: "example"
author: "Scout Leonard"
date: '2022-04-20'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(rvest)
library(tidyverse)
```

Point to URL:

```{r}
url <- "https://ucsb-meds.github.io/overview.html"
```

Read the html:

```{r}
html <- read_html(url)
```

HTML elements allows you to pull an element associated with a specific tag. 

`html_text()` gives us a vector that contains strings that we can use with a package like `tidy_text`. 

```{r}
#pull paragraphs
paragraphs <- html %>% 
  html_elements("p") #looks for the paragraph element

paragraph_vector <- paragraphs %>% 
  html_text()

#pull titles 
titles <- html %>% 
  html_elements("title")


```

It can be helpful to pull an leement then use `html_text()` to convert elements to a more usable format. 

```{r}
level2_headers <- html %>% 
  html_elements("h2")

level2_headers %>% html_text() #gives us a nicer format: vector of level 2 headers 
```

If you want to use tabular data in an html document, `html_table()` can be helpful:

```{r}
tables <- html %>% 
  html_elements("table")

tables_clean <- html_table(html) #makes a nice tibble! 

tables_clean[[1]] #if there is more than one table on a page, access the desired table by indexing the list of tables 
```


